### 2017-10-08 reorganize/papers/elliott-thesis/latex/thesis.tex
Add stuff which should have been in previous commit

\thesistitle{Simulating dynein'’s powerstroke using Brownian dynamics} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Dr. David \textsc{Roundy}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Bachelor of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Elliott \textsc{Capek}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\AtBeginDocument{
\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
\hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
}

@@

\HRule \\[0.4cm] % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm] % Horizontal line

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
  \caption{Artist's rendition of dynein bound to a microtubule.}{Two heavy chains (cyan and blue) and several tail proteins (pink) come together to form the dynein motor complex. One monomer's binding domain is bound to the microtubule (green), and the other is diffusing. ATP hydrolysis sites are labeled glowing green. Figure modified. Source: Lander Lab, The Scripps Research Institute \cite{landerartistsrendition}.}
  \label{dynein-artist-rendition}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
%%   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion constant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
%%   \label{fig:diffusion_vs_dynein}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/retrograde_transport.jpg}
  \caption{Dynein transport to neuron growth cones.}{Dynein and kinesin collaborate to move cargo between the neuron body and axon tip. The oppositely-directed motors take turns transporting each other, along with cargo for building the axon growth cone. Image from \cite{valetoolbox}.}
  \label{retrograde-transport}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth,keepaspectratio]{../../figures/pdb-motm-dynein}
  \caption{Structure of a dynein monomer.}{A cryo-electron microscopy-inspired image detailing the subcomponents of a single dynein monomer. The microtubule-binding domain (MTBD) connects to the motor domain via a coiled coil known as the stalk. The six AAA regions provide structure for the motor domain, and AAA2 conducts the ATP hydrolysis. The linker is a flexible region which connects the motor domain to the tail. One of the main roles of the tail is connecting a monomer to its twin to form the dynein complex. Image from \cite{pdb-motm-dynein}.}
  \label{fig:pdb-motm-dynein}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{../../figures/weihong-step-size}
  \includegraphics[width=0.49\textwidth]{../../figures/weihong-off-axis-steps}
    \caption{Experimental dynein stepping behavior histograms.}{Left: Size of steps taken by dynein motor parallel to microtubule. Positive axis corresponds to steps towards the microtubule minus-end. Right: Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule. Figure modified from \cite{weihongpaper}.}
  \label{fig:weihong-steps}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein}
  \end{minipage}
  \begin{minipage}{0.65\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein_2}
  \end{minipage}
  \caption{Structural comparison of dynein and kinesin}{Left: Comparison of crystal structures of the motor domains of dynein and kinesin bound to a microtubule. Image from \cite{kinesin-vs-dynein}. Right: Full motor complexes of dynein and kinesin inspired by cryo-EM microscopy. The blue regions on the right image of either protein are the motor domains, which are pictured in the left crystal structures. Not present in the left cyrstal structures are the tail and intermediate chains of either protein. Right image from \cite{kinesin-vs-dynein-2}.}
  \label{fig:kinesin-vs-dynein}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/burgess-dynein-angles}\\
  \hspace{1cm}
  \includegraphics[width=.95\textwidth,keepaspectratio]{../../figures/linker-swing}
  \caption{Dynein conformation change during a step.}{Top: Cryo-electron microscopy images of axonemal dynein in two different nucleotide states. Top left: dynein frozen in ADP-Pi state. Top middle: dynein without nucleotide. Top right: two states superimposed on one another. Figures from \cite{burgess-paper}. Bottom: X-ray diffraction-inspired image of a motor in two nucleotide states. Bottom left: motor in ADP-Pi state. Bottom right: Motor in ADP state. The linker undergoes an approximately 40 degree swing between these two states known as the powerstroke. Figure from \cite{bhabha-paper}.}
  \label{fig:cryo-em-angles}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.90\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
  \newcommand\transition{\textcolor{green}{transition?}}
  %% \begin{tabular}{rll}
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     Bound to microtubule and waiting for ATP to arrive.  The
  %%     conformation is ``post-powerstroke''.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   2 & \begin{minipage}{5in}
  %%     ATP has bound to the motor at AAA1, but nothing else has changed.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \transition &
  %%   3 & \begin{minipage}{5in}
  %%     ``The ring has closed'' in the motor, whatever that means.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   4 & \begin{minipage}{5in}
  %%     The affinity to the microtubule is dropped, so it is likely to pop off soon.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   5 & \begin{minipage}{5in} It has popped off of the microtubule!
  %%     Onebound! The equilibrium angle is also changed.  The ATP has
  %%     been hydrolized, but the phosphate is still bound to the motor.
  %%     ``Priming stroke?''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   6 & \begin{minipage}{5in} It is now bound to the microtubule, but
  %%     with low affinity, and without any loss of phosphate. Question:
  %%     does this happen many times? If so it may still be onebound.
  %%     Otherwise it is probably bothbound.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   7 & \begin{minipage}{5in}
  %%     Now it is seriously bound to the microtubule, and the motor
  %%     domain has changed conformation.  This is now ``high affinity.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   8 & \begin{minipage}{5in}
  %%     Phosphate has been released, and our equilibrium angles have
  %%     been changed.  This is the ``power stroke.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     The ADP has been released from the motor domain, so it can now
  %%     bind ATP.  Still ``high affinity,'' and still in the
  %%     ``power-stroke'' conformation.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   9 & \begin{minipage}{5in}
  %%     While stuck in this ``normal bound'' state, another site on the
  %%     motor AAA3 can lose its ADP, which leaves the motor in a state
  %%     where it cannot directly move on to step 2 (until after
  %%     reversing this).  Controversial?
  %%   \end{minipage}
  %% \end{tabular}
  \caption{Cianfrocco mechanochemical cycle.}{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/theory-onebound}
  \includegraphics[width=.45\textwidth]{../../figures/theory-bothbound}
  \caption{Spatial representation of the dynein dynamic model.}{Dynein is simplified to two two-dimensional point-particle systems. The left ``onebound'' system represents dynein when one MTBD is unbound, and the right ``bothbound'' system represents dynein with both MTBDs bound. Five points in total represent the two MTBDs, two motor domains and one tail domain. Each model's orientation is defined by a set of angles, four in the onebound case and two in the bothbound case. These points are connected by rigid rods. Although approximated as points, each domain has a radius $R$ associated with it used for drag calculations.}
  \label{fig:theory-intro}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/ob_fig}
%%   \caption{Onebound dynein model.}{}
%%   \label{fig:model-intro}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth]{../../figures/angular-spring}
  \caption{Angular spring return force when out of equilibrium.}{The $\theta_{bb}$ angle shown is greater than the equilibrium angle $\theta_{bb}^{eq}$, and thus the $bb$ domain has conformational energy $\frac{1}{2}c_b\left(\theta_{bb}-\theta_{bb}^{eq}\right)^2$, and feels a force pulling the motor domain towards the microtubule.}
  \label{fig:angular-spring}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/derivation-onebound}
  \caption{Spatial representation of the onebound dynein model.}{The coordinate system used for derivation of onebound forces.}
  \label{fig:derivation-onebound}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/derivation-bothbound}
  \caption{Spatial representation of the bothbound dynein model.}{The coordinate system used for derivation of bothbound forces.}
  \label{fig:derivation-bothbound}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
%%   \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
%%   \label{fig:sarlah-rate-table}
%% \end{figure}

@@

%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
%%     \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
%%   \end{minipage}
%%   \hspace{.2cm}
%%   \begin{minipage}[b]{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
%%   \end{minipage}
%%   \label{fig:equipartition_agreement}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\textwidth]{../../plots/trajectory-plot_thesis}
  \caption{Dynein simulation displays processive stepping.}{Near and far binding domain x and y projections over the course of several microseconds of simulation. The blue foot corresponds to the ``near'' dimer closer to the viewer, and the red to the far dimer. Top: x-projection of binding domains over time. The motor steps roughly 50nm in 10 $\mu s$. Middle: cartoon depictions of the model during simulation. In the cartoons the blue foot's position on the x-axis corresponds to the time axis on the top and bottom plots. That is, the first cartoon corresponds to dynein at roughly 1 $\mu s$. The first cartoon corresponds to a bothbound model, and the second cartoon corresponds to a onebound model. Bottom: y-projection of binding domains over time. Notice that only one binding domain is above 0nm at any time.}
  \label{fig:stepping-trajectory}
\end{figure}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
    \caption{Stepping distribution of processive model and experimental dynein.}{Left: step sizes generated by model. Note the model can generate 25nm steps, but has a high preference for <5nm steps. Also note that few backward steps are generated by the model. Simulation run at conditions in (\ref{table:thesis-parameters}). Right: Experimental stepping distribution of dynein, from \cite{weihongpaper}.}
    \label{fig:final-histograms}
\end{figure}

@@

%% \begin{figure}[H]
%%   \centering
%%   \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
%%   \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$. The fit quality of each simulation is decided by $\log_{10}\left(\frac{\left<t_{bb}\right>_{sim}}{\left<t_{bb}\right>_{exp}}\right)$, then fit to the colorbar on the right. Values over or under the colorbar bounds are rounded to the max (1.0 or -1.0).}
%%   \label{fig:kb-kub-heatmap}
%% \end{figure}

>>>>

%% \newcommand{\ttitle}{Simulating dynein's powerstroke using Brownian dynamics}
%% \newcommand{\title}{Simulating dynein's powerstroke using Brownian dynamics}
%% \thesistitle{Simulating dynein'’s powerstroke using Brownian dynamics} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle

\newcommand{\ttitle}{Thesis title}
\makeatletter
\renewcommand{\@title}{Thesis title}
\makeatother

\supervisor{Dr. David \textsc{Roundy}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Bachelor of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Elliott \textsc{Capek}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\AtBeginDocument{
%% \hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
\hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
}

@@

\HRule \\[0.4cm] % Horizontal line
%% {\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm] % Horizontal line

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/dynein-artist-rendition.jpg}
  \caption{Artist's rendition of dynein bound to a microtubule.}{Two heavy chains (cyan and blue) and several tail proteins (pink) come together to form the dynein motor complex. One monomer's binding domain is bound to the microtubule (green), and the other is diffusing. ATP hydrolysis sites are labeled glowing green. Figure modified. Source: Lander Lab, The Scripps Research Institute \cite{landerartistsrendition}.}
  \label{dynein-artist-rendition}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
%%   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion constant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
%%   \label{fig:diffusion_vs_dynein}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/retrograde_transport.jpg}
  \caption{Dynein transport to neuron growth cones.}{Dynein and kinesin collaborate to move cargo between the neuron body and axon tip. The oppositely-directed motors take turns transporting each other, along with cargo for building the axon growth cone. Image from \cite{valetoolbox}.}
  \label{retrograde-transport}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth,keepaspectratio]{../figures/pdb-motm-dynein}
  \caption{Structure of a dynein monomer.}{A cryo-electron microscopy-inspired image detailing the subcomponents of a single dynein monomer. The microtubule-binding domain (MTBD) connects to the motor domain via a coiled coil known as the stalk. The six AAA regions provide structure for the motor domain, and AAA2 conducts the ATP hydrolysis. The linker is a flexible region which connects the motor domain to the tail. One of the main roles of the tail is connecting a monomer to its twin to form the dynein complex. Image from \cite{pdb-motm-dynein}.}
  \label{fig:pdb-motm-dynein}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/weihong-step-size}
  \includegraphics[width=0.49\textwidth]{../figures/weihong-off-axis-steps}
    \caption{Experimental dynein stepping behavior histograms.}{Left: Size of steps taken by dynein motor parallel to microtubule. Positive axis corresponds to steps towards the microtubule minus-end. Right: Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule. Figure modified from \cite{weihongpaper}.}
  \label{fig:weihong-steps}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio]{../figures/kinesin_vs_dynein}
  \end{minipage}
  \begin{minipage}{0.65\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio]{../figures/kinesin_vs_dynein_2}
  \end{minipage}
  \caption{Structural comparison of dynein and kinesin}{Left: Comparison of crystal structures of the motor domains of dynein and kinesin bound to a microtubule. Image from \cite{kinesin-vs-dynein}. Right: Full motor complexes of dynein and kinesin inspired by cryo-EM microscopy. The blue regions on the right image of either protein are the motor domains, which are pictured in the left crystal structures. Not present in the left cyrstal structures are the tail and intermediate chains of either protein. Right image from \cite{kinesin-vs-dynein-2}.}
  \label{fig:kinesin-vs-dynein}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/burgess-dynein-angles}\\
  \hspace{1cm}
  \includegraphics[width=.95\textwidth,keepaspectratio]{../figures/linker-swing}
  \caption{Dynein conformation change during a step.}{Top: Cryo-electron microscopy images of axonemal dynein in two different nucleotide states. Top left: dynein frozen in ADP-Pi state. Top middle: dynein without nucleotide. Top right: two states superimposed on one another. Figures from \cite{burgess-paper}. Bottom: X-ray diffraction-inspired image of a motor in two nucleotide states. Bottom left: motor in ADP-Pi state. Bottom right: Motor in ADP state. The linker undergoes an approximately 40 degree swing between these two states known as the powerstroke. Figure from \cite{bhabha-paper}.}
  \label{fig:cryo-em-angles}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.90\textwidth,keepaspectratio]{../figures/mechanochemical-cycle.jpeg}
  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
  \newcommand\transition{\textcolor{green}{transition?}}
  %% \begin{tabular}{rll}
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     Bound to microtubule and waiting for ATP to arrive.  The
  %%     conformation is ``post-powerstroke''.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   2 & \begin{minipage}{5in}
  %%     ATP has bound to the motor at AAA1, but nothing else has changed.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \transition &
  %%   3 & \begin{minipage}{5in}
  %%     ``The ring has closed'' in the motor, whatever that means.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   4 & \begin{minipage}{5in}
  %%     The affinity to the microtubule is dropped, so it is likely to pop off soon.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   5 & \begin{minipage}{5in} It has popped off of the microtubule!
  %%     Onebound! The equilibrium angle is also changed.  The ATP has
  %%     been hydrolized, but the phosphate is still bound to the motor.
  %%     ``Priming stroke?''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   6 & \begin{minipage}{5in} It is now bound to the microtubule, but
  %%     with low affinity, and without any loss of phosphate. Question:
  %%     does this happen many times? If so it may still be onebound.
  %%     Otherwise it is probably bothbound.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   7 & \begin{minipage}{5in}
  %%     Now it is seriously bound to the microtubule, and the motor
  %%     domain has changed conformation.  This is now ``high affinity.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   8 & \begin{minipage}{5in}
  %%     Phosphate has been released, and our equilibrium angles have
  %%     been changed.  This is the ``power stroke.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     The ADP has been released from the motor domain, so it can now
  %%     bind ATP.  Still ``high affinity,'' and still in the
  %%     ``power-stroke'' conformation.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   9 & \begin{minipage}{5in}
  %%     While stuck in this ``normal bound'' state, another site on the
  %%     motor AAA3 can lose its ADP, which leaves the motor in a state
  %%     where it cannot directly move on to step 2 (until after
  %%     reversing this).  Controversial?
  %%   \end{minipage}
  %% \end{tabular}
  \caption{Cianfrocco mechanochemical cycle.}{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/theory-onebound}
  \includegraphics[width=.45\textwidth]{../figures/theory-bothbound}
  \caption{Spatial representation of the dynein dynamic model.}{Dynein is simplified to two two-dimensional point-particle systems. The left ``onebound'' system represents dynein when one MTBD is unbound, and the right ``bothbound'' system represents dynein with both MTBDs bound. Five points in total represent the two MTBDs, two motor domains and one tail domain. Each model's orientation is defined by a set of angles, four in the onebound case and two in the bothbound case. These points are connected by rigid rods. Although approximated as points, each domain has a radius $R$ associated with it used for drag calculations.}
  \label{fig:theory-intro}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/ob_fig}
%%   \caption{Onebound dynein model.}{}
%%   \label{fig:model-intro}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth]{../figures/angular-spring}
  \caption{Angular spring return force when out of equilibrium.}{The $\theta_{bb}$ angle shown is greater than the equilibrium angle $\theta_{bb}^{eq}$, and thus the $bb$ domain has conformational energy $\frac{1}{2}c_b\left(\theta_{bb}-\theta_{bb}^{eq}\right)^2$, and feels a force pulling the motor domain towards the microtubule.}
  \label{fig:angular-spring}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/derivation-onebound}
  \caption{Spatial representation of the onebound dynein model.}{The coordinate system used for derivation of onebound forces.}
  \label{fig:derivation-onebound}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/derivation-bothbound}
  \caption{Spatial representation of the bothbound dynein model.}{The coordinate system used for derivation of bothbound forces.}
  \label{fig:derivation-bothbound}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.45\textwidth]{../figures/SarlahParameterTable.png}
%%   \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
%%   \label{fig:sarlah-rate-table}
%% \end{figure}

@@

%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
%%     \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
%%   \end{minipage}
%%   \hspace{.2cm}
%%   \begin{minipage}[b]{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
%%   \end{minipage}
%%   \label{fig:equipartition_agreement}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\textwidth]{../../../plots/trajectory-plot_thesis}
  \caption{Dynein simulation displays processive stepping.}{Near and far binding domain x and y projections over the course of several microseconds of simulation. The blue foot corresponds to the ``near'' dimer closer to the viewer, and the red to the far dimer. Top: x-projection of binding domains over time. The motor steps roughly 50nm in 10 $\mu s$. Middle: cartoon depictions of the model during simulation. In the cartoons the blue foot's position on the x-axis corresponds to the time axis on the top and bottom plots. That is, the first cartoon corresponds to dynein at roughly 1 $\mu s$. The first cartoon corresponds to a bothbound model, and the second cartoon corresponds to a onebound model. Bottom: y-projection of binding domains over time. Notice that only one binding domain is above 0nm at any time.}
  \label{fig:stepping-trajectory}
\end{figure}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{../../../plots/stepping_length_histogram_thesis}%%
    \includegraphics[width=0.5\textwidth]{../figures/weihong-step-size.pdf}
    \caption{Stepping distribution of processive model and experimental dynein.}{Left: step sizes generated by model. Note the model can generate 25nm steps, but has a high preference for <5nm steps. Also note that few backward steps are generated by the model. Simulation run at conditions in (\ref{table:thesis-parameters}). Right: Experimental stepping distribution of dynein, from \cite{weihongpaper}.}
    \label{fig:final-histograms}
\end{figure}

@@

%% \begin{figure}[H]
%%   \centering
%%   \includegraphics[width=\textwidth]{../figures/kb-kub-contour}
%%   \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$. The fit quality of each simulation is decided by $\log_{10}\left(\frac{\left<t_{bb}\right>_{sim}}{\left<t_{bb}\right>_{exp}}\right)$, then fit to the colorbar on the right. Values over or under the colorbar bounds are rounded to the max (1.0 or -1.0).}
%%   \label{fig:kb-kub-heatmap}
%% \end{figure}
